### 2021-11-21 thesis/tex/ICtheory.tex
update

In Fig.~\ref{fig:IC_MC_norm}, we present the Icecube Monte Carlo obtained from their 2020 sterile analysis~\cite{IC2020}, along
with our null hypothesis times a constant factor. 
We used the best-fit values from NuFit~\cite{nufit} with the exception of the CP-violating phase $\delta_\text{CP}$, which was set to $0$ for simplicity. The values used are
\begin{align}\label{eq:nufitparams}
    \theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
\end{align}

>>>>

In Fig.~\ref{fig:IC_MC_norm}, we present the IceCube Monte Carlo obtained from their 2020 sterile analysis~\cite{IC2020}, along
with our null hypothesis times a constant factor. 
We used the best-fit values from NuFit~\cite{nufit} with the exception of the CP-violating phase $\delta_\text{CP}$, which was set to $0$ for simplicity. The values used are
\begin{align}\label{eq:nufitparams}
    \theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
\end{align}
